\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using a Shared Input

### 2018-01-18 journalWallFriction/theory2robAlgs.tex
new abstract and 3D text

\subsection{3D model}

Extending to 3D is straight forward, but possible only if the two particles do not have the same $x$ and $y$ positions. Fig.~\ref{fig:zaxis} shows a cylinder. The blue particle is in the blue plate and the red robot is in the red plate. There are two possible optimal paths shown with parallel arrows. 
Each arrow will cause one of the particles to touch the wall, enabling the other robot to move freely in $z$ axis to make the required relative position.

>>>>

\subsection{3D workspaces: Cylinders and Prisms}

Extending path planning to 3D is possible only if the two particles do not initially have the same $x$ and $y$ positions.
For ease of analysis, we assume the workspace boundaries extend in the $\pm z$ direction to form either right cylinders or right prisms.
If the 3D projection is at a different angle, redefine the 2D workspace as a region perpendicular to the projection.
 First, we move the closest particle to the boundary, which prevents its $z$ coordinate from changing.  
 We next apply actuation in either the $\pm z$ direction to achieve the desired $\Delta z$.
 Then the particles are actuated away from the boundary and to the appropriate $z$ positions.
 Path planning continues using Alg. XX to position the particles to the desired $x$ and $y$ positions. 
 As an example, consider Fig.~\ref{fig:zaxis} which shows a cylinder.
 The blue particle starts in the blue disk and the red particle starts in the red disk. There are two possible optimal paths shown with parallel arrows. 
Each arrow will cause one of the particles to touch the wall, enabling the other robot to move freely in the  $z$ axis to achieve the required relative position.
This can be extended to other 3D workspaces if the workspace can be locally approximated as a 3D prism or cylinder. Other workspaces may be better handled by other path planners, such as \cite{MassiveUnifromManipulation}.
